\sout{Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body} \ZZ{Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques}

### 2020-02-04 jfm/draft_p2_jfm.tex
Add pdf
Add appendix on AMS

In practice, we started by fixing the computational cost associated with a single run of the cloning algorithm, \textit{i.e.} by fixing $N \times T_a$.
Consistently with section~\ref{sec:time_avg}, we aim at sampling trajectories with a duration $T = 10\tau_c$.
Consequently, we fixed $T_a = 15\tau_c$ to allow for an initial transient regime of the cloning algorithm.
Then, we chose $N = 1024$ to obtain a computational cost of order $\mathcal{O}(10^4 \tau_c)$, \textit{i.e.} roughly one hundredth of the computational cost associated with the direct numerical simulation used for direct sampling in section~\ref{sec:direct_sampling}.
Finally, we set $\tau = \tau_c / 2$.
\textbf{How do we set k?}

@@

% algo
%
The complexity of the flow emerges from the repeated application of simple rules of streaming and collision. The \ac{lbm} advances the local densities of particles $f_i(\mathbf{x},t)$ moving with velocities $\mathbf{c}_i$  in a two-step procedure. Namely, an \emph{exact} streaming step
\[
f_i(\mathbf{x}+\mathbf{c}_i \Delta t, t + \Delta t) = f_i^{\mathrm{out}}(\mathbf{x},t)
\]
during which particles move with their own velocity to a neighbouring node, and an instantaneous collision step
\[
f_i^{\mathrm{out}}(\mathbf{x},t) = -\frac 1 {\tau_\nu} \left(f_i(\mathbf{x},t) - f_i^\mathrm{eq}(\mathbf{x},t) \right)
\]
which achieves a relaxation of local densities towards an absolute equilibrium (at the macroscopic level). The time-scale $\tau_\nu$ (in lattice unit) is related to the kinematic viscosity of the fluid by
\[
\nu = \left( {\tau_\nu} - \frac 1 2 \right) c_s^2 ~\Delta t
\]
This simplification of the collision kernel is known as the BGK approximation in the kinetic theory of gas \EL{\citep{BGK}}.
%
The equilibrium function is given by
\[
f_i^\mathrm{eq}(\mathbf{x},t) = w_i  \rho(\mathbf{x},t) \left( 1 + \frac{\mathrm u(\mathbf{x},t) \cdot \mathbf{c_i}}{c_s^2} +
\frac{u_\alpha(\mathbf{x},t) u_\beta(\mathbf{x},t)({c_i}_\alpha {c_i}_\beta - c_s^2 \delta_{\alpha\beta})}{2 c_s^4} \right)
\]
with the weight factors $w_0=4/9,~w_{1...4} = 1/9$ and $w_{5...8}=1/36$ for the D2Q9 lattice.
This discrete Lattice Boltzmann scheme is second-order accurate in $\Delta x $ and compliant to the weakly-compressible Navier-Stokes equations with a third-order error in $\mathrm{Ma}=|\mathbf{u}|/c_s$ as the lattice spacing vanishes, i.e. $\Delta x \to 0$ \EL{\citep{succi_book}}.

@@

>>>>

In practice, we started by fixing the computational cost associated with a single run of the cloning algorithm, \textit{i.e.} by fixing $N \times T_a$.
Consistently with section~\ref{sec:time_avg}, we aim at sampling trajectories with a duration $T = 10\tau_c$.
Consequently, we fixed $T_a = 15\tau_c$ to allow for an initial transient regime of the cloning algorithm.
Then, we chose $N = 1024$ to obtain a computational cost of order $\mathcal{O}(10^4 \tau_c)$, \textit{i.e.} roughly one hundredth of the computational cost associated with the direct numerical simulation used for direct sampling in section~\ref{sec:direct_sampling}.
Finally, we set $\tau = \tau_c / 2$.
\textbf{Thibault: Explain the choice of k}

@@

% algo
%
The complexity of the flow emerges from the repeated application of simple rules of streaming and collision. The \ac{lbm} advances the local densities of particles $f_i(\mathbf{x},t)$ moving with velocities $\mathbf{c}_i$  in a two-step procedure. Namely, an \emph{exact} streaming step
\begin{equation}
  \label{eq:lbe}
  f_i(\mathbf{x}+\mathbf{c}_i \Delta t, t + \Delta t) = f_i^{\mathrm{out}}(\mathbf{x},t)
\end{equation}
during which particles move with their own velocity to a neighbouring node, and an instantaneous collision step
\[
f_i^{\mathrm{out}}(\mathbf{x},t) = -\frac 1 {\tau_\nu} \left(f_i(\mathbf{x},t) - f_i^\mathrm{eq}(\mathbf{x},t) \right)
\]
which achieves a relaxation of local densities towards an absolute equilibrium (at the macroscopic level). The time-scale $\tau_\nu$ (in lattice unit) is related to the kinematic viscosity of the fluid by
\[
\nu = \left( {\tau_\nu} - \frac 1 2 \right) c_s^2 ~\Delta t
\]
This simplification of the collision kernel is known as the BGK approximation in the kinetic theory of gas \EL{\citep{BGK}}.
%
The equilibrium function is given by
\begin{equation}
  \label{eq:lbe_eq}
  f_i^\mathrm{eq}(\mathbf{x},t) = w_i  \rho(\mathbf{x},t) \left( 1 + \frac{\mathrm u(\mathbf{x},t) \cdot \mathbf{c_i}}{c_s^2} +
    \frac{u_\alpha(\mathbf{x},t) u_\beta(\mathbf{x},t)({c_i}_\alpha {c_i}_\beta - c_s^2 \delta_{\alpha\beta})}{2 c_s^4} \right),
\end{equation}
with the weight factors $w_0=4/9,~w_{1...4} = 1/9$ and $w_{5...8}=1/36$ for the D2Q9 lattice.
This discrete Lattice Boltzmann scheme is second-order accurate in $\Delta x $ and compliant to the weakly-compressible Navier-Stokes equations with a third-order error in $\mathrm{Ma}=|\mathbf{u}|/c_s$ as the lattice spacing vanishes, i.e. $\Delta x \to 0$ \EL{\citep{succi_book}}.

@@

\include{appendix_ams}
